Group 5 Report

### 2022-08-03 Report/Group 5 report v2.Rmd
saved this time

```{r, echo=FALSE, fig.cap="Need caption"}
# Illustration some text some pictures in financial statements
knitr::include_graphics("Images/lagret_tekst.png") # Kreftforeningen 201?
knitr::include_graphics("Images/lagret_bilde.png") # Regnskogfondet 2018
```

@@

```{r, echo=FALSE, fig.cap="Need caption", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Brns_items.png")
knitr::include_graphics("Images/OPX_items.png")
knitr::include_graphics("Images/Marriage.png")
```

@@

```{r, echo=FALSE, out.width="100%", fig.cap="Need caption"}
# Illustration only published for some years example
knitr::include_graphics("Images/Regnskogfondet_stops2018.png")
knitr::include_graphics("Images/Kreftforeningen_starts2019.png")
```

@@

```{r, echo=FALSE, out.width="100%", fig.cap="Need caption"}
# Bilde av den "endelige" excel-versjonen som brukes til å laste inn i shiny
knitr::include_graphics("Images/Excel_final.png")
```

@@

```{r egenkapital, echo=FALSE, fig.align='center', fig.asp=0.5, fig.cap="Total equity/liabilities (in NOK 1,000) data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  scale_fill_green(kreftforeningen$balance_positive) +
  labs(
    x = "", y = ""
  ) +
  theme_light() +
  theme(legend.position = "none")
```

```{r CEO, echo=FALSE, fig.align='center', fig.asp=0.618, fig.cap="CEO compensation data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  # preparing for pivoting
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |>
  # Compensation in ordinary numbers
  mutate(
    lederlonn = lederlonn * 1000,
    leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
  ) |>
  # renaming for the purposes of the plot
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |>
  # pivoting to join the two values to use fill
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  # using currency scale function to add correct currency code or ?
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  # pretty colours
  scale_fill_met_d("Hokusai2", direction = -1) +
  labs(
    x = "", y = ""
  ) +
  theme_light() +
  theme(legend.position = "top")
```

>>>>

```{r, echo=FALSE, fig.cap="Kreftforeningen 2021: The financial report saved as text in the PDF"}
# Illustration some text some pictures in financial statements
knitr::include_graphics("Images/lagret_tekst.png") # Kreftforeningen 2021
```

```{r, echo=FALSE, fig.cap="Regnskogfondet 2018: The financial report saved as an image in the PDF"}
# Illustration some text some pictures in financial statements
knitr::include_graphics("Images/lagret_bilde.png") # Regnskogfondet 2018
```

@@

```{r, echo=FALSE, fig.cap="Accounting items for Kreftforeningen 2020 and Diabetesforbunet 2020, gathered from the Brønnøysund registry", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Brns_items1.png")
```

```{r, echo=FALSE, fig.cap="Accounting items for Kreftforeningen 2020 and Diabetesforbunet 2020, gathered from OPX", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/OPX_items1.png")
```

```{r, echo=FALSE, fig.cap="An attempt at marrying the two sets of accounting items", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Marriage.png")
```

@@

```{r, echo=FALSE, out.width="100%", fig.cap="Regnskogfondet stopped posting financial statement PDFs on their website in 2018"}
# Illustration only published for some years example
knitr::include_graphics("Images/Regnskogfondet_stops2018.png")
```

```{r, echo=FALSE, out.width="100%", fig.cap="Kreftforeningen started posting financial statement PDFs on their website in 2019"}
# Illustration only published for some years example
knitr::include_graphics("Images/Kreftforeningen_starts2019.png")
```

@@

```{r, echo=FALSE, out.width="100%", fig.cap="The data format used to upload into shiny"}
# Bilde av den "endelige" excel-versjonen som brukes til å laste inn i shiny
knitr::include_graphics("Images/Excel_final.png")
```

@@
